Blog post: Identifying and manipulating non-breaking spaces

### 2020-02-05 text/20/non-breaking-space.Rmd
Cleaning up odd symbols, part 4
Fixed problem with Rmd files

![![Figure 1. Screenshot of a file inside Notepad](non-breaking-space01.png not found.](../../../web/images/20/non-breaking-space.Rmd01.png)

@@

![![Figure 2. Screenshot of a file inside RStudio](non-breaking-space02.png not found.](../../../web/images/20/non-breaking-space.Rmd02.png)

@@

So what are these pink dots, exactly? I used cut and paste to insert this strange character into a character string in R

>>>>

![Figure 1. Screenshot of the file inside Notepad](../../../web/images/20/non-breaking-space01.png)

@@

![![Figure 2. Screenshot of the file inside RStudio](../../../web/images/20/non-breaking-space02.png)

@@

So what are these pink dots, exactly? I used cut-and-paste to insert this strange character into a character string in R.
